Draft

### 2020-09-16 Final.Rmd
finished changing FSR to CLS (except figure 1,2,3). more text changes to follow

As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts. A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007). Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020). Among all these investigations, it is the censored likelihood score (CLS) or the focused score (FSR) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management. In other words, CLS/FSR allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.

@@

Both LS and CRPS are used for producing and evaluating the entire predictive densities. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as in $\eqref{eq:fsr}$
\begin{equation} \label{eq:fsr}
S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
\end{equation}
where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$. Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

@@

\begin{equation} \label{eq:theta}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{equation}
\begin{equation} \label{eq:score}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{equation}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:FSR}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]

\begin{equation} \label{eq:LS}
S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{equation}
\begin{equation} \label{eq:CRPS}
S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{equation}
\begin{equation} \label{eq:FSR}
S_{FSR}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{equation}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{equation} \label{eq:avgscore}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{equation}

@@

GARCH_t12 <- read.csv("GARCH_t12__table.csv")
GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

GARCH_t3 <- read.csv("GARCH_t3_table.csv")
GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

ARCH_table <- read.csv("ARCH_table.csv")
ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
ARCH_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

Copula5_table <- read.csv("Copula5_table.csv")
Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
Copula5_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

Copula3_table <- read.csv("Copula3_table.csv")
Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
Copula3_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

Copula0_table <- read.csv("Copula0_table.csv")
Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
Copula0_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

@@

```{r}
ARCH_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
```

```{r}
GARCH_t12 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 2: the true DGP is GARCH(1,1) with degree of freedom = 12"=7))
```

```{r}
GARCH_t3 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with degree of freedom = 3"=7))
```

@@

Copula0_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 4: the true DGP is copula with shape parameter = 0"=7))
```

```{r}
Copula3_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 5: the true DGP is copula with shape parameter = -3"=7))
```

```{r}
Copula5_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 6: the true DGP is copula with shape parameter = -5"=7))
```

@@

From Table 1, the correct specification case, we could observe coherence and strict coherence in Table 3 when the degree of model misspecification is high. These results are consistent with conclusions from Loiaza-Maya et al. (2020). It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions. That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.

@@

The predictive accuracy of tails is important for financial risk management. Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails. The results in Section 3.2.1 shows that when the degree of model misspecification is high, FSR can perform the best compared with MLE and CRPS in predicting tails. However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.

In the left panel of each trace plot, it shows the performance of each score evaluated by FSR 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From Figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE in predicting tails. The more misspecified the model is, the more benefits can we gain from using FSR. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

@@

We still use ARCH(1) model in Section 3 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility. More importantly, it is misspecified with a high degree of model misspecification. Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution. The results of Table 8 support our conjecture. However, the difference between using FSR10(80) and FSR20(90) is very small.

```{r}
sp_table <- read.csv("sp_table.csv")
sp_table <- rename(sp_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
sp_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 8: Average scores for S&P 500"=7))
```

@@

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
trace_fsr10 <- read.csv("fsr10.csv")
trace_fsr20 <- read.csv("fsr20.csv")
trace_10ls <- read.csv("fsr10_ls.csv")
trace_10crps <- read.csv("fsr10_crps.csv")

@@

color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")

>>>>

As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts. A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007). Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020). Among all these investigations, it is the censored likelihood score (CLS) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management. In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.

@@

Both LS and CRPS are used for producing and evaluating the entire predictive densities. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as in $\eqref{eq:cls}$
\begin{equation} \label{eq:cls}
S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
\end{equation}
where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$. Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

@@

\begin{equation} \label{eq:theta}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{equation}
\begin{equation} \label{eq:score}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{equation}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]

\begin{equation} \label{eq:LS}
S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{equation}
\begin{equation} \label{eq:CRPS}
S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{equation}
\begin{equation} \label{eq:CLS}
S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{equation}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{equation} \label{eq:avgscore}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{equation}

@@

GARCH_t12 <- read.csv("GARCH_t12__table.csv")
GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

GARCH_t3 <- read.csv("GARCH_t3_table.csv")
GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

ARCH_table <- read.csv("ARCH_table.csv")
ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
ARCH_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

Copula5_table <- read.csv("Copula5_table.csv")
Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
Copula5_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

Copula3_table <- read.csv("Copula3_table.csv")
Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
Copula3_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

Copula0_table <- read.csv("Copula0_table.csv")
Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
Copula0_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

@@

```{r}
ARCH_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
```

```{r}
GARCH_t12 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 2: the true DGP is GARCH(1,1) with degree of freedom = 12"=7))
```

```{r}
GARCH_t3 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with degree of freedom = 3"=7))
```

@@

Copula0_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 4: the true DGP is copula with shape parameter = 0"=7))
```

```{r}
Copula3_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 5: the true DGP is copula with shape parameter = -3"=7))
```

```{r}
Copula5_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 6: the true DGP is copula with shape parameter = -5"=7))
```

@@

From Table 1, the correct specification case, we could observe coherence and strict coherence in Table 3 when the degree of model misspecification is high. These results are consistent with conclusions from Loiaza-Maya et al. (2020). It simply means that we can improve prediction accuracy by using CLS in the presence of model misspecification under certain conditions. That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.

@@

The predictive accuracy of tails is important for financial risk management. Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails. The results in Section 3.2.1 shows that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting tails. However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.

In the left panel of each trace plot, it shows the performance of each score evaluated by CLS 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From Figure 1 and 2, we could see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, CLS starts to outperform CRPS and MLE in predicting tails. The more misspecified the model is, the more benefits can we gain from using CLS. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

@@

We still use ARCH(1) model in Section 3 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility. More importantly, it is misspecified with a high degree of model misspecification. Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing CLS do a better job in predicting two tails of the distribution. The results of Table 8 support our conjecture. However, the difference between using CLS10(80) and CLS20(90) is very small.

```{r}
sp_table <- read.csv("sp_table.csv")
sp_table <- rename(sp_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
sp_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 8: Average scores for S&P 500"=7))
```

@@

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
# this is assessed by cls10 for prediction accuracy
trace_fsr10 <- read.csv("fsr10.csv")
trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
trace_fsr20 <- read.csv("fsr20.csv")
trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
trace_10ls <- read.csv("fsr10_ls.csv")
trace_10crps <- read.csv("fsr10_crps.csv")

@@

color1 <- c("CLS10"="red","CLS20"="black","MLE"="purple","CRPS"="green")
